Paper on the carbonate chemistry at Ny-Ålesund

### 2020-12-21 paper.Rmd
fixed figure time series

d_ts <- d %>%
  dplyr::mutate(pH_s_seafet_temp_ctd = ifelse(depth >= 8, pH_s_seafet_temp_ctd, NA)) %>% # keep only seafet data below 8 m depth
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air_filtered, PCO2_Corr_filtered, pH_s_seafet_temp_ctd, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

@@

# PAR
ts_par_air <- d_all %>%
  ggplot(aes(x = datetime, y = par_air_filtered), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
  Mytheme(size_labs = 8)

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_contros), 
             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = pco2calc), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = 8)

# SEAFET pH
ts_pH <- d_all %>%
  ggplot(aes(x = datetime, y = pH_s_seafet_temp_ctd), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="In situ pH (> 8 m)",x="", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = 8)

>>>>

d_ts <- d %>%
  #dplyr::mutate(pHint_tot_sf = ifelse(depth >= 8, pHint_tot_sf, NA)) %>% # keep only seafet data below 8 m depth
  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_corr,
                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
  #tidyr::pivot_longer(-datetime, values_to = "value")

@@

# PAR
ts_par_air <- d_all %>%
  ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
  Mytheme(size_labs = 8)

# PCO2 
ts_pCO2 <- d_all %>%
  ggplot() +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(aes(x = datetime, y = pco2_corr), 
             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
  Mytheme(size_labs = 8)

# SEAFET pH
ts_pH <- d_all %>%
  ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
  labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
  Mytheme(size_labs = 8)
